\section*{\large Proposed Title}
\textbf{Your Research Title Here}


\section*{\large Students Agreement}
\parbox{\textwidth}{
	By signing below on \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ \_ , we, as Group \_ \_ \_ \_ members, agree to the terms of the CST 395-2 Research Methodology and Scientific Writing course at the 300 level. We commit to conducting the research project titled as mentioned above and outlined in the agreement. We understand that any changes to the group composition, identified research problem, or selected supervisor may result in penalties.\\
	
	\begin{tabularx}{\textwidth}{|l|l|X|}
		\hline
		\textbf{Name} & \textbf{Registration Number} & \multicolumn{1}{c|}{\textbf{Signature}} \\
		\hline
		Mr. Initials1 Surname1 & UWU/CST/20/001 & \\[10pt] % Increase row height
		\hline	
		Ms. Initials2 Surname2 & UWU/CST/20/002 & \\[10pt] % Increase row height
		\hline
		Mr. Initials3 Surname3 & UWU/CST/20/003 & \\[10pt] % Increase row height
		\hline	
		Ms. Initials4 Surname4 & UWU/CST/20/004 & \\[10pt] % Increase row height
		\hline
	\end{tabularx}
}


\section*{\large Supervisor Agreement}
\parbox{\textwidth}{
	I/We agree to supervise the above group of students throughout their research project, providing guidance and support for successful completion. I/We acknowledge that changes to group composition, identified research problem, or responsibilities may require further discussion.\\
	
	\begin{tabularx}{\textwidth}{|l|X|X|}
		\hline
		\textbf{Name} & \multicolumn{1}{c|}{\textbf{Signature}} & \multicolumn{1}{c|}{\textbf{Date}}  \\
		\hline
		Dr. Initials1 Surname1 &  & \\[10pt] % Increase row height	
		\hline		
		Mr. Initials2 Surname2 &  & \\[10pt] % Increase row height
		\hline		
		Ms. Initials3 Surname3 &  & \\[10pt] % Increase row height
		\hline
	\end{tabularx}
}