\section{Research Methodology}

First, give a small introduction to the section - briefly mention your philosophical things here (e.g., positivism, pragmatism)

\subsection{Research Approach and Strategy}
Explain whether your study will adopt a qualitative, quantitative, or mixed methods approach. Justify your choice based on the nature of your research questions and objectives.

\subsection{Data Collection Methods}
Outline the methods you will use to collect data. This may include surveys, interviews, observations, experiments, or archival research. Explain why these methods are appropriate for your study.

\subsection{Sampling Strategy}
Describe your sampling strategy, including the population or sample size, sampling technique, and any inclusion or exclusion criteria. Justify your sampling decisions based on the characteristics of your target population and the objectives of your study.

\subsection{Data Analysis Techniques}
Explain the analytical techniques you will use to analyze your data. This may include statistical analysis, thematic analysis, content analysis, or other qualitative or quantitative methods. Justify your choice of analysis techniques based on the nature of your data and research questions.

\subsection{Ethical Considerations}
Discuss any ethical considerations related to your research, such as informed consent, confidentiality, privacy, and potential risks to participants. Explain how you will address these ethical concerns to ensure the welfare of participants and the integrity of your study.

\subsection{Evaluation Strategy}
Describe metrics, baseline comparisons, validations, tools/frameworks, and how success is planned to measure.

\subsection{Tools and Technologies}
Mention specific tools, platforms, libraries, and hardware planned to use.
